Leadership across cultures and contexts: an exploratory analysis

### 2020-05-14 leadership_across_cultures_contexts.Rmd
Minor edit in conclusion.

<!-- DAVIDS MARKET FORCES IDEAS -->
We agree with @pietraszewski_evolution_2019 that leadership and followership stem from biological market forces and information-processing roles [e.g., @garfield_evolutionary_2019; @hagen_leadership_2019], however, much of human leadership goes beyond group coordination problems, such as leaders important roles in devising strategic outcomes between individuals, offering advice or decision-making services to individuals, and in making direct prosocial investments that do not involve substantial coordination. We therefore suggest leadership dynamics emerge from inter-individual competencies and leaders' abilities to provide benefits *or* impose costs, with these dimensions interacting with market forces rooted in follower preferences, group context, and cultural norms. 
 <!-- Whereas @pietraszewski_evolution_2019 emphasizes leaders ability to propose various enterprises and followers ability to evaluate them, -->

>>>>

<!-- DAVIDS MARKET FORCES IDEAS -->
We agree with @pietraszewski_evolution_2019 that leadership and followership stem from biological market forces and information-processing roles [e.g., @garfield_evolutionary_2019; @hagen_leadership_2019], however, much of human leadership goes beyond group coordination problems, such as leaders important roles in devising strategic outcomes between individuals, offering advice or decision-making services to one or a few individuals, and in making prosocial community investments that do not involve substantial coordination. We therefore suggest leadership dynamics emerge from inter-individual competencies and leaders' abilities to provide benefits *or* impose costs, with these dimensions interacting with market forces rooted in follower preferences, group context, and cultural norms. 
 <!-- Whereas @pietraszewski_evolution_2019 emphasizes leaders ability to propose various enterprises and followers ability to evaluate them, -->
